Assesing Health Care Coverage and Access Utilizing the National Health Interview Survey

### 2017-03-08 paper/paper.tex
finished paper

Final summary and a description of how your system could be extended.

>>>>

Our motivation to focus on healthcare was influenced from our class
discussions, guest speakers, and even or own personal experiences as
healthcare beneficiaries. We observe how the life of other individuals
are impacted by the opportunities to attain healthcare coverage. Through
our research project studied how health expenditure changed from
2005-2015 for individuals. Our findings help support that idea
individuals are mostly spending about less than five-hundred dollars per
year on medical charges. This information could be helpful to help
develop better health care options to target this population, as they
seem to represent a bigger portion of those who spend between
five-hundred to roughly five-thousand dollars per year.

Another finding of our research consisted of how of an impact did
education attainment have on healthcare access. One point of interest in
the educational system was high school. High school was a point that
indicated a change in healthcare accessibility. Those who went to pursue
higher education were observed to attain their coverage through their
workforce. This is something that differs from the idea that higher
education leads to more money which ultimately implies that you access
for healthcare coverage from your own earnings. It is interesting to
realize that the workforce could influence a person access to
healthcare.

Our last section of research consisted of the overall population and how
the proportions of healthcare coverage can differ. We realize that the
proportion of those who have some sort of healthcare coverage is larger
than the proportion of those who lack coverage. This, in our
perspective, is a positive finding as it is an indicator that more
people have access to healthcare. A final suggestion of our study is
that we hope to gain more information on the process of government's
funding. To be more specific we want to gain information on the exact
journey that government funds travel. We wish to know how certain
policies contribute to the healthcare funding of diverse organizations.
Our hopes to to find where government funding is increasing the
accessibility of healthcare coverage for any individual that wished to
attain it.
